---
title: "Appendix"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE}
#Load Packages
library(tidyverse)
library(knitr)
library(stargazer)

#Laod the Data Set
mc_carbon_df <- read_csv("HW4Data.csv")
mc_carbon_df

#Notes About Data
#Current carbon emissions in the sectors are: (A=180, B=200, C=220, and D=300).
#Sectors A, B, and C are in country X. Sector D is in a different country, Y.
#Prices are in $/ton and quantities are in tons.

```

##I. Marginal Carbon Abatement Costs and Demand 

###1. Marginal Abatement Costs
-A linear regression model was utilized to determine the marginal cost of abatement of carbon for each sector.

-At any quantity, x, the marginal cost of abatement can be obtained using the appropriate function and substracting "x" from the current emissions scenario. 

-Within the linear regression model, subtracting a quantity of "0" from the current level of emissions for each sector attained the marginal willingness to pay for the first unit of carbon abatement.

-Thus the current level of emissions was inserted into each sector's function to determine this customer willingness to pay when (x=0). 

-The demand curves for each sector were determined through sequential marginal willingness to pay estimations.

####Sector "A"
```{r, include = FALSE}
#Create Function with Linear Regression
#Plot the Points and Regression Line
paris_plotA <- ggplot(mc_carbon_df, aes(x = mc_carbon_df$Abatement, y = mc_carbon_df$MC_A)) + geom_point() + geom_smooth(method = "lm")
paris_plotA

#Find the Equation of the Line
paris_modelA <- lm(MC_A ~ Abatement, data = mc_carbon_df)
coef(paris_modelA)

# Intercept for Sector "A"
int_a <- -8.6444767

#Slope for Sector "A"
slope_a <- 0.5768419

```
a. $Marginal~Abatement~Cost(A) = -8.6444767 + 0.5768419(Tons~of~Abatement)$
b. $WTP~at~Current~Emissions(A) = -8.6444767 + 0.5768419(180-x)$
c. Sector A is willing to pay $95.19 for the first unit of abatement


####Sector "B"
```{r, include=FALSE}
#Create Function with Linear Regression
#Plot the Points and Regression Line
paris_plotB <- ggplot(mc_carbon_df, aes(x = mc_carbon_df$Abatement, y = mc_carbon_df$MC_B)) + geom_point() + geom_smooth(method = "lm")
paris_plotB

#Find the Equation of the Line
paris_modelB <- lm(MC_B ~ Abatement, data = mc_carbon_df)
coef(paris_modelB)


#Intercept for Sector "B"
int_b <- 9.3176977

#Slope for Sector "B"
slope_b <- 0.1987443 

```
a. $Marginal~Abatement~Cost(B) = 9.3176977 + 0.1987443(Tons~of~Abatement)$
b. $WTP~at~Current~Emissions(B) = 9.3176977 + 0.1987443(200-x)$
c. Sector B is willing to pay $49.07 for the first unit of abatement


####Sector "C"
```{r, include = FALSE}
#Create Function with Linear Regression
#Plot the Points and Regression Line
paris_plotC <- ggplot(mc_carbon_df, aes(x = mc_carbon_df$Abatement, y = mc_carbon_df$MC_C)) + geom_point() + geom_smooth(method = "lm")
paris_plotC

#Find the Equation of the Line
paris_modelC <- lm(MC_C ~ Abatement, data = mc_carbon_df)
coef(paris_modelC)

# Intercept for Sector "C"
int_c <- -11.6550307 

#Slope for Sector "C"
slope_c <- 0.7838266

```
a. $Marginal~Abatement~Cost(C) = -11.6550307 + 0.7838266(Tons~of~Abatement)$
b. $WTP~at~Current~Emissions(C) = -11.6550307 + 0.7838266(220-x)$
c. Sector C is willing to pay $160.79 for the first unit of abatement
d. Sector C is willing to pay the most for abatement


####Sector "D"
```{r, include = FALSE}
#Create Function with Linear Regression
#Plot the Points and Regression Line
paris_plotD <- ggplot(mc_carbon_df, aes(x = mc_carbon_df$Abatement, y = mc_carbon_df$MC_D)) + geom_point() + geom_smooth(method = "lm")
paris_plotD

#Find the Equation of the Line
paris_modelD <- lm(MC_D ~ Abatement, data = mc_carbon_df)
coef(paris_modelD)

# Intercept for Sector "D"
int_d <- 9.6875061

#Slope for Sector "D"
slope_d <- 0.2599275

```
a. $Marginal~Abatement~Cost(D) = 9.6875061 + 0.2599275(Tons~of~Abatement)$
b. $WTP~at~Current~Emissions(D) = 9.6875061 + 0.2599275(300-x)$
c. Sector D is willing to pay $87.67 for the first unit of abatement



```{r, echo = FALSE, message = FALSE, include = FALSE}
#Create a "tidy" Data Frame
colnames(mc_carbon_df) <- c("Abatement", "A", "B", "C", "D")

carbon_tidy <- mc_carbon_df %>% 
  gather(Sector, Price, A:D) 
```

###2. Graphical Representation of Marginal Abatement Costs 
```{r, echo = FALSE, warning = FALSE, message = FALSE}
#Create a Plot of All Sectors

paris_plot_all <- ggplot(carbon_tidy, aes(x = Abatement, y = Price)) + geom_point() + geom_smooth(method = "lm", title = "Marginal Abatement Costs by Sector", color = "red4") + facet_wrap(~Sector) + theme_classic() + ggtitle("Marginal Abatement Costs by Sector") + labs(x = "Abatement (tons of carbon)", y = "Price ($/ton)")

paris_plot_all


```



```{r, message = FALSE, echo = FALSE, warning = FALSE, include = FALSE}
####Regression Results
regression_results <- stargazer(paris_modelA, paris_modelB, paris_modelC, paris_modelD, type="text", title="Table 1: Marginal Abatement Cost Regression Results")

```



```{r, include = FALSE}
###Demand Curves and WTP at Current Levels of Emissions 
#Marginal Abatement Costs at Current Emissions
mccurrent_A <- -8.6444767 + (0.5768419*180)
mccurrent_B <- 9.3176977 + (0.1987443*200)
mccurrent_C <- -11.6550307 + (0.7838266*220)
mccurrent_D <- 9.6875061 + (0.2599275*300)


#WTP for the First Unit 
mccurrent_A #$95.18707
mccurrent_B #$49.06656
mccurrent_C #$160.7868
mccurrent_D #$87.66576


(mccurrent_A-0)/0.5768419
(mccurrent_B-0)/0.1987443
(mccurrent_C-0)/0.7838266
(mccurrent_D-0)/0.2599275



```

```{r, include = FALSE}
#Derive Demand Curve of Sector A

# Use Quantities from 0 to 180 by 5 to Estimate a Demand Curve
vector_demand_A <- seq(0,180,by=5)
# Write function for demand curve for Sector A
demand_A_function <- function(x){(slope_a*(180-x)) + int_a}


# Derive demand curve using the values above
demand_A <- demand_A_function(vector_demand_A)
demand_A

# Graph it to see if this worked....
demand_A_gph <- curve(demand_A_function, from=0, to=180, xlab = "x", ylab = "y")

#Derive Demand Curve of Sector B

# Use Quantities from 0 to 200 by 5 to Estimate a Demand Curve
vector_demand_B <- seq(0,200,by=5)
# Write function for demand curve for Sector A
demand_B_function <- function(x){(slope_b*(200-x)) + int_b}


# Derive demand curve using the values above
demand_B <- demand_B_function(vector_demand_B)
demand_B

# Graph it to see if this worked....
demand_B_gph <- curve(demand_B_function, from=0, to=200, xlab = "x", ylab = "y")

#Derive Demand Curve of Sector C

# Use Quantities from 0 to 220 by 5 to Estimate a Demand Curve
vector_demand_C <- seq(0,220,by=5)
# Write function for demand curve for Sector A
demand_C_function <- function(x){(slope_c*(220-x)) + int_c}


# Derive demand curve using the values above
demand_C <- demand_C_function(vector_demand_C)
demand_C

# Graph it to see if this worked....
demand_C_gph <- curve(demand_C_function, from=0, to=220, xlab = "x", ylab = "y")

#Derive Demand Curve of Sector D

# Use Quantities from 0 to 300 by 5 to Estimate a Demand Curve
vector_demand_D <- seq(0,300,by=5)
# Write function for demand curve for Sector A
demand_D_function <- function(x){(slope_d*(300-x)) + int_d}


# Derive demand curve using the values above
demand_D <- demand_D_function(vector_demand_D)
demand_D

# Graph it to see if this worked....
demand_D_gph <- curve(demand_D_function, from=0, to=300, xlab = "x", ylab = "y")




#Find all new Demand Curves at Current Level
#Use new points to find new slopes


slope_a_d <- -0.5768419
slope_b_d <- -0.2453285
slope_c_d <- -0.7308526
slope_d_d <- -0.2922217

mccurrent_A #$95.18707 or intercept
mccurrent_B #$49.06656 or intercept
mccurrent_C #$160.7868 or intercept
mccurrent_D #$87.66576 or intercept

```


```{r, message = FALSE, echo = FALSE, warning=FALSE, include = FALSE}
demand_plot <- ggplot(data.frame(x = c(0, 350))) + 
  stat_function(fun = demand_A_function, aes(color = "A")) +
  stat_function(fun = demand_B_function, aes(color = "B")) +
  stat_function(fun = demand_C_function, aes(color = "C")) +
  stat_function(fun = demand_D_function, aes(color = "D")) +
  scale_y_continuous(limits= c(-12,170), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 400), expand = c(0,0)) + 
  labs(fill = "", color = "Sectors") + 
  xlab("\nAbatement (ton)") + 
  ylab("Marginal Cost \n($/ton) \n") + 
  theme_classic() +
  ggtitle("Demand of the Marginal Cost of Carbon Abatement\n") +
  theme(plot.title = element_text(hjust = 0.5),
        axis.title.y = element_text(angle=90, hjust = 0.5, vjust = 0.5)) 
demand_plot


#$$MC_A = -0.5768419(Emissions) + 95.18707$$
#$$MC_B = -0.2453285(Emissions) + 49.06656 $$
#$$MC_C = -0.7308526Emissions) + 160.7868 $$
#$$MC_D = -0.2922217(Emissions)+ 87.66576 $$


```

##Cutting Carbon Emissions in Half: Analyzing 3 Policies for Country X
####1. Policy Option: A Cap on Carbon

```{r include=FALSE}
# Each sector cuts emissions by 100 - abates 100 
################# Part 1 Write abatement curve functions for each sector and plug in 100 for Q
#### Abatement function Sector A
Abatement_curve_A <- function(x){(slope_a*x) + int_a}
cost_100_A <- Abatement_curve_A(100) 
cost_100_A

#### Abatement function Sector B
Abatement_curve_B <- function(x){(slope_b*x) + int_b}
cost_100_B <- Abatement_curve_B(100)
cost_100_B

#### Abatement function Sector C
Abatement_curve_C <- function(x){(slope_c*x) + int_c}
cost_100_C <- Abatement_curve_C(100)
cost_100_C 

#### Abatement function Sector D (USE LATER)
Abatement_curve_D <- function(x){(slope_d*x) + int_d}
cost_100_D <- Abatement_curve_D(100)
cost_100_D 



################## Part 2 Integrate to find the area under the curve (the cost of abatement from 0-100)
area_100_A <- integrate(Abatement_curve_A, lower = 0, upper = 100)$value
area_100_A #$2019.762
area_100_B <- integrate(Abatement_curve_B, lower = 0, upper = 100)$value
area_100_B #$1925.491
area_100_C <- integrate(Abatement_curve_C, lower = 0, upper = 100)$value
area_100_C #$2753.63

################## Part 3 Add all areas together to find the total cost of abating 100 units from each sector
total_cost_abatement_100 <- area_100_A + area_100_B + area_100_C
tca <- round(total_cost_abatement_100, digits =2) #6698.883
tca
```

Marginal cost of abatement curves for each sector are used to calculate the total cost of abating by 100 tons. The area underneath the marginal cost of abatement curve from 0 to 100 gives the total cost of abatement for that sector. The total cost of carbon cap is the sum of the costs of three sectors.

a. Total Cost of Carbon Cap     

The total cost of the carbon cap is $6698.88 


b. The Total Cost of a Carbon Cap for Each Sector      

The total cost for Sector A is  $2019.76 

The total cost for Sector B is  $1925.49 

The total cost for Sector C is  $2753.63


c. The Tax Revenue Generated from a Carbon Cap  

There is no tax revenue generated with a carbon cap



####2. Policy Option: A Tax on Carbon

```{r, include = FALSE}
#Find the Demand Curves for Each Sector and Switch in Terms of X to find Aggregate Demand

#For Sector A
A_demand_x_intercept <- (-int_a/slope_a)
A_demand_x_slope <- (1/slope_a)
A_demand_tax <- function(p){A_demand_x_intercept + A_demand_x_slope*p}


#For Sector B
B_demand_x_intercept <- (-int_b/slope_b)
B_demand_x_slope <- (1/slope_b)
B_demand_tax <- function(p){B_demand_x_intercept + B_demand_x_slope*p}


#For Sector C
C_demand_x_intercept <- (-int_c/slope_c)
C_demand_x_slope <- (1/slope_c)
C_demand_tax <- function(p){C_demand_x_intercept + C_demand_x_slope*p}


#For Sector D (USE LATER)
D_demand_x_intercept <- (-int_d/slope_d)
D_demand_x_slope <- (1/slope_d)
D_demand_tax <- function(p){D_demand_x_intercept + D_demand_x_slope*p}

#Add the Demand Curves Together to Find the Aggregate
Agg_demand_intercept <- sum(A_demand_x_intercept, B_demand_x_intercept, C_demand_x_intercept)
Agg_demand_slope <- sum(A_demand_x_slope, B_demand_x_slope, C_demand_x_slope)


#Switch the Aggregate Demand Curve Back in terms of P (price)
Agg_demand_p_intercept <- (-Agg_demand_intercept/Agg_demand_slope)
Agg_demand_p_slope <- (1/Agg_demand_slope)
Agg_demand_curve_tax <- function(x){Agg_demand_p_intercept + Agg_demand_p_slope*x}


#Find the Optimal Tax by Inputting Desired Level of Emissions (300 Tons)
optimal_tax <- Agg_demand_curve_tax(300)
optimal_tax

#Find the Tax Revenue by Multiplying times the Optimal Emissions
tax_revenue_tax <- optimal_tax*300
tax_revenue_tax


#Find the Cost for Each Sector

#The Cost for Sector A
# Sector A 
quantity_abatement_A <- A_demand_tax(optimal_tax)
quantity_abatement_A # 83.33489
cost_A_tax <- integrate(Abatement_curve_A, lower = 0, upper = quantity_abatement_A)$value + ((180-83.3)*optimal_tax)
cost_A_tax

# Sector B 
quantity_abatement_B <- B_demand_tax(optimal_tax) 
quantity_abatement_B # 151.4956
quantity_abatement_B*optimal_tax
cost_B_tax <- integrate(Abatement_curve_B, lower = 0, upper = quantity_abatement_B)$value + ((200-151.5)*optimal_tax)
cost_B_tax

# Sector C 
quantity_abatement_C <- C_demand_tax(optimal_tax) 
quantity_abatement_C #65.16953
cost_C_tax <- integrate(Abatement_curve_C, lower = 0, upper = quantity_abatement_C)$value + ((220-65.2)*optimal_tax)
cost_C_tax

# Aggregated cost
cost_agg_tax <- sum(cost_A_tax, cost_B_tax, cost_C_tax)
cost_agg_tax
```

a. The Total Cost of a Carbon Tax

The optimal tax is $39.43

This tax is equal to the marginal cost of abatement for the 300th ton of carbon for Country "X" when the desired abatement (300 tons) is substituted into the aggregate demand function for all sectors. 

The total cost of a carbon tax is $17707.79


b. The Total Cost of a Carbon Tax for Each Sector

The cost to Sector A is $5095.16

The cost to Sector B is $5604.46

The cost to Sector C is $7008.16


c. The Tax Revenue Generated from a Carbon Tax

The total tax revenue is $11827.97


```{r, include=FALSE}
# Sector A 
#Abates 83.33489 and buys (100-83.33489) from Sector B
cost_A_cap <- integrate(Abatement_curve_A, lower = 0, upper = quantity_abatement_A)$value + ((100-83.33489)*optimal_tax)
cost_A_cap # $1939.66


# Sector B 
 #Abates 151.4956 and sells (200-151.4956) to A and C
cost_B_cap <- integrate(Abatement_curve_B, lower = 0, upper = quantity_abatement_B)$value - ((200-151.4956)*optimal_tax)
cost_B_cap # $1779.909


# Sector C 
# Abates 65.16953 and buys (100-65.16953) from B
cost_C_cap <- integrate(Abatement_curve_C, lower = 0, upper = quantity_abatement_C)$value + ((100-65.16953)*optimal_tax)
cost_C_cap # $2278.176


cost_Agg_cap<- cost_A_cap + cost_B_cap + cost_C_cap
cost_Agg_cap # $5997.744
#costagg_cap <- integrate(agg_abate, lower = 0, upper = 300)$value
```
####3. Policy Option: A Cap and Trade Program

a. The Total Cost of a Carbon Cap and Trade Program

The total cost of a carbon cap and trade program is $5997.74


b. The Total Cost of a Carbon Cap and Trade Program for Each Sector

The cost to Sector A is $1939.66

The cost to Sector B is $1779.91

The cost to Sector C is $2278.18


c. The Tax Revenue Generated from a Carbon Tax

There is no tax revenue generated with cap and trade program 


##Country "Y"" Joining the Carbon Market of Country "X""

```{r include = FALSE}
#Find the Demand Curves for Sector D and Switch in Terms of X to add to Aggregate Demand

#Demand Curve
D_demand_x_intercept <- (-int_d/slope_d)
D_demand_x_slope <- (1/slope_d)

#Integrate into Aggregate
agg_int_x_XY <- Agg_demand_intercept + D_demand_x_intercept
agg_slope_x_XY <- Agg_demand_slope + D_demand_x_slope


# Put in terms of price:
agg_price_abatement_XY <- function(x){((1/agg_slope_x_XY)*x) + (abs(agg_int_x_XY)/agg_slope_x_XY)}


# Find optimal tax/marginal cost of 300 with 300
cost_xy <- agg_price_abatement_XY(300)
cost_xy # $29.80249


#Sector A
q_xy_A <- A_demand_tax(cost_xy)
q_xy_A #abates 66.65079, buys (100-66.65079)  
cost_A_xy <- integrate(Abatement_curve_A, lower = 0, upper = q_xy_A)$value + ((100-66.65079)*cost_xy)
cost_A_xy #1698.989

# Sector B 
q_xy_B <- B_demand_tax(cost_xy)
q_xy_B #abates $103.0711, sells
cost_B_xy <- integrate(Abatement_curve_B, lower = 0, upper = q_xy_B)$value - ((103.0711-100)*cost_xy)
cost_B_xy # $1924.554

# Sector C 
q_xy_C <- C_demand_tax(cost_xy)
q_xy_C# abates 52.89119 buys (100-52.89119)
cost_C_xy <- integrate(Abatement_curve_C, lower = 0, upper = q_xy_C)$value + ((100-52.89119)*cost_xy)
cost_C_xy # $1883.88


#Sector D
q_xy_D <- D_demand_tax(cost_xy)
q_xy_D# abates 77.38691, sells all
cost_D_xy <- integrate(Abatement_curve_D, lower = 0, upper = q_xy_D)$value - (77.38691*cost_xy)
cost_D_xy # $-778.3183


cost_agg_xy<-cost_A_xy + cost_B_xy + cost_C_xy + cost_D_xy
cost_agg_xy # $4729.105


```

1. The Total Cost of a Carbon Cap and Trade Program with Both Countries

The total cost of a carbon cap and trade program is $4729.11


2. The Total Cost of a Carbon Cap and Trade Program for Each Sector

The cost to Sector A is $1698.99

The cost to Sector B is $1924.55

The cost to Sector C is $1883.88

The benefit to Sector D is $778.32


3. The Tax Revenue Generated from a Carbon Tax

There is no tax revenue generated with cap and trade program.


Country "Y" is incentivised to join the market with Country "X" because it will have a benefit of $778.32 if it sells all of its carbon credits to the other three sectors.  While the sectors in Country "X" still have to purchase under the cap and trade program, the addition of Country "Y" lowers the marginal cost of abatement for each ton of carbon.  Without the addition of Sector D, the marginal cost of abatement for Country "X" is 39.43 dollars, whereas with Country "Y" it is only 29.80 dollars for 300 tons. Thus Country "X" is incentivised to welcome Sector D into its market. 

##Air Pollution
 

```{r include=FALSE}
total_emission_x <- 300 + q_xy_D
total_emission_x
```



```{r include=FALSE}
total_emission_y <- 300-q_xy_D
total_emission_y
```
a. In a market of just Country "X" the local air pollution would be 300 tons. (300 tons carbon emissions*1 ton local air pollution). If Country "Y" is not limited by cap and trade it will emits current scenario of 300 tons of carbon, also generating 300 tons of local pollutants.

b. If Country "Y" joins the Cap and Trade Program, Country "X" will be emitting more carbon. Thus its local pollution will rise from 300 tons to 377.39 tons after purchasing the 77.39 abatement tons from Country "Y".  Since Country "Y" sells some of its carbon emissions, it will have less local pollution.  Its local air pollution will be reduced from 300 tons to 222.61 tons.